---
output: github_document
bibliography: "man/packages.bib"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readmat

<!-- badges: start -->
[![R-CMD-check](https://github.com/MartinSchobben/readmat/workflows/R-CMD-check/badge.svg)](https://github.com/MartinSchobben/readmat/actions)
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
[![license](https://img.shields.io/github/license/mashape/apistatus.svg)](https://choosealicense.com/licenses/mit/)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
<!-- badges: end -->

Readmat requires  a full license and installation of Matlab^(R)^ if you don't have this then the `R.matlab` [@R.matlab] package is much more suitable. The only goal of this package is to provide a potentially faster approach, especially when dealing with large matrices.

This package is definitely under development!

## Benchmark

A data cube of 400 x 400 x 400 values.

```{r examplee} 
readmat::read_mat(readmat::get_matlab("double-large-cube.mat"))[[1]] |> 
  dim()
```

Comparing `R.matlab` and `readmat`.

```{r bench, echo=FALSE}
# powered by bench::mark()
knitr::kable(readmat:::bm, digits=2)
```

## Installation

You can install the development version of readmat from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MartinSchobben/readmat")
```

## Credits

```{r pkgs, echo=FALSE, message=FALSE, eval=FALSE}
# following code for loading and writing the bibtex references for the used pkgs
pkgs <- c("R.matlab", "cpp11", "devtools")  
# Get the R reference
rref <- citation()
# Create ref key
rref$key <- "rversion"
# write bib
knitr::write_bib(pkgs, "man/packages.bib", prefix = "")
pkgs <- bibtex::read.bib("man/packages.bib")
bibtex::write.bib(
  purrr::reduce(list(rref, pkgs), append), 
  file = "man/packages.bib"
)
```

The construction of the R [@rversion] package `readmat` and associated documentation was aided by the packages; `devtools` [@devtools] and `cpp11` [@cpp11].

# References
