---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readmat

<!-- badges: start -->
<!-- badges: end -->

Readmat requires  a full license and installation of Matlab^(R)^ if you don't have this then the `R.matlab` package is much more suitable. The only goal of this package is to provide a potentially faster approach, especially when dealing with large matrices.

This package is definitely under development!

## Benchmark

A data cube of 400 x 400 x 400 values.

```{r examplee} 
readmat::read_mat(readmat::get_matlab("double-large-cube.mat"))[[1]] |> 
  dim()
```

Comparing `R.matlab` and `readmat`.

```{r bench, echo=FALSE}
# powered by bench::mark()
knitr::kable(readmat:::bm, digits=2)
```

## Installation

You can install the development version of readmat from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MartinSchobben/readmat")
```

